The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-12 paper/paper.tex
blah

\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 

@@

Galaxy formation
simulations can reproduce present-day galaxies with notably different assembly and star formation histories.  

@@

factors of order  unity, and even binary neutron star populations differ by tens of percent.  

>>>>

%\title{Details matter: Similar host galaxies can harbor different merging compact binary populations} 
\title{The effects of host galaxy properties on merging compact binaries detectable by LIGO}

@@

Cosmological simulations of galaxy formation can produce present-day galaxies with a large range assembly and star formation histories.  A detailed study of the metallicity evolution and star formation history of such simulations can assist in predicting LIGO-detectable compact object binary mergers.

@@

factors of order  unity, and even binary neutron star populations differ by tens of percent.  \jillianremark{add sentence about mass dependence (more in dwarfs).}
